\LARGE \bf The Battle for Filter Supremacy: A Comparative Study of the Multi-State Constraint Kalman Filter and Sliding Window Filter

### 2014-12-30 Report/project_report.tex
Transposed table and added IMU only bit

\begin{table*}[t]
  \centering
    \caption{Comparison of Average Root Mean Squared Error (ARMSE), Average Normalized Estimation Error Squared (ANEES), and Compute Time of the MSCKF and SWF on synthetic datasets.}
  \begin{tabular}{*{11}{c}}
              && \multicolumn{4}{c}{MSCKF} & & \multicolumn{4}{c}{SWF} \B \\ \cline{3-6} \cline{8-11}
Feature Count && Pos. ARMSE & Rot. ARMSE & ANEES   & Compute Time && Pos. ARMSE & Rot. ARMSE & ANEES & Compute Time \T\B \\ \hline
40            && 0.2672        & 0.1378        & 10.18  &              && 0.1750        & 0.0495        & 2280 &    \T \\
60            && 0.2550        & 0.1247        & 12.03  &              && 0.1687        & 0.0377        & 2093 &    \\
100           && 0.2304        & 0.0952        & 16.76  &              && 0.1755        & 0.0481        & 2013 &    \B \\ \hline
  \end{tabular}
  \label{tab:rmse_nees}
\end{table*}

@@

Although the SWF appears to be more accurate than the MSCKF,

>>>>

% \begin{table*}[t]
%   \centering
%     \caption{Comparison of Average Root Mean Squared Error (ARMSE), Average Normalized Estimation Error Squared (ANEES), and Compute Time of the MSCKF and SWF on synthetic datasets.}
%   \begin{tabular}{*{11}{c}}
%               && \multicolumn{4}{c}{MSCKF} & & \multicolumn{4}{c}{SWF} \B \\ \cline{3-6} \cline{8-11}
% Feature Count && Pos. ARMSE    & Rot. ARMSE & ANEES     & Compute Time && Pos. ARMSE   & Rot. ARMSE     & ANEES & Compute Time \T\B \\ \hline
% 40            && 0.2672        & 0.1378        & 10.18  & 12.19 s      && 0.1750        & 0.0495        & 2280  & 114.3 s   \T \\
% 60            && 0.2550        & 0.1247        & 12.03  & 14.64 s      && 0.1687        & 0.0377        & 2093  & 175.9 s   \\
% 100           && 0.2304        & 0.0952        & 16.76  & 20.58 s      && 0.1755        & 0.0481        & 2013  & 245.3 s   \B \\ \hline
%   \end{tabular}
%   \label{tab:rmse_nees}
% \end{table*}

\begin{table}
    \centering
    \caption{Comparison of Average Root Mean Squared Error (ARMSE), Average Normalized Estimation Error Squared (ANEES), and Compute Time of IMU integration, MSCKF, and SWF on synthetic datasets.}
    \begin{tabular}{*{5}c} 
                    &                   & \multicolumn{3}{c}{Feature Count} \B      \\ \cline{3-5}
                    &                   & 40        & 60        & 100       \T\B    \\ \hline
        IMU Only    & Position ARMSE    & 0.3679    & 0.3679    & 0.3679    \T      \\
                    & Rotation ARMSE    & 0.1452    & 0.1452    & 0.1452            \\
                    & ANEES             & 0.2850    & 0.2850    & 0.2850            \\
                    & Compute Time      & 8.90 s    & 8.90 s    & 8.90 s    \B      \\ \hline
        MSCKF       & Position ARMSE    & 0.2672    & 0.2550    & 0.2304    \T      \\
                    & Rotation ARMSE    & 0.1378    & 0.1247    & 0.0952            \\
                    & ANEES             & 10.18     & 12.03     & 16.76             \\
                    & Compute Time      & 12.19 s   & 14.64 s   & 20.58 s   \B      \\ \hline
        SWF         & Position ARMSE    & 0.1750    & 0.1687    & 0.1755    \T      \\
                    & Rotation ARMSE    & 0.0495    & 0.0377    & 0.0481            \\
                    & ANEES             & 2280      & 2093      & 2013              \\
                    & Compute Time      & 114.3 s   & 175.9 s   & 245.3 s   \B      \\ \hline
    \end{tabular}
    \label{tab:rmse_nees}
\end{table}

@@

Although the SWF appears to produce more accurate pose estimates than the MSCKF in many cases, the MSCKF has the advantage of being less computationally intensive than the SWF, and of having better consistency properties.
The MSCKF may be a better choice of algorithm in situations where computational resources are limited, or where a consistent estimate of state uncertainty is desirable.
